### 2018-11-15 papers/journal/encoding.tex
added QBF section and attached Synthesis encodings to it

\externaldocument{sat-table}
\externaldocument{smt-table}

@@

\subsection{Boolean satisfiability of the search problem}

@@

\begin{enumerate}
	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between $i$ and $j$.
\end{enumerate}

@@

In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
%
Nondeterminism can be considered as an oracle that guesses a correct $m$-path for a specific m if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule m on every edge E.
%

\subsubsection{Constraints for stability condition}
%
We use NOracle to guess the required path to encode the stability condition in VTS.
%
The following constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
The NOracle perform enumeration of $m$-${paths}_i^j$ of at most w length. 
%
Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length w-1.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] >> m) > 0) \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

@@

\subsection{Universal condition}

>>>>

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}

@@

%\subsection{Boolean satisfiability of the search problem}

@@

\begin{enumerate}
	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
\end{enumerate}

@@

In order to specify the stability condition, we use a combination of enumeration and nondeterminism.
%
Nondeterminism can be viewed as an oracle that guesses a correct $m$-path for a specific m if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule m on every edge E.
%

\subsubsection{Constraints for stability condition}
%
We use NOracle to guess the required path to encode the stability condition in VTS.
%
A naive implementation of NOracle is shown in~\ref{eq:reachbmc1}.
%
The constraint encodes that there is a $m$-path from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of $m$-${paths}_i^j$ of at most w length. 
%
Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length w-1.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
%
We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

@@

\subsection{Universal condition}
Recall that the specification for universal condition~\ref{eq:univcond} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
\todo{SA: Rewrite completely}But it is still possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
% 
We have implemented a SAT version with the current encoding of the same.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
This may blow up the formula size for the solver to solve.

\input{qbf-table}
%
In the table~\ref{tab:satqbf-graph}, you can see that SAT version was not able to scale it to the desired results.
%
This is due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.

\textbf{QBF encoding of universal condition:}
We will describe several constraints that encode VTSs in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

The following constraints encode the basic consistency of VTSs. 
%
Recall that now the molecule set is divided into 3:1 Q and R pairs (or partition).
\begin{align*}
\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\land
\bigwedge\limits_{i,q} \neg e_{i,i,q}
\land
% \tag{\texttt{NodeC}}\label{eq:f0}\\
\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\\
\texttt{ActivityC} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
% \tag{V2}\label{eq:f1}\\
\\
\texttt{PairingC} =\;&
\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
% \bigwedge\limits_{m} 
% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
\\
\texttt{Fusion1} =\;&
\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
\\
\texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
& \hspace{2cm} \neg 
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\\
\texttt{Consistancy} =\;& \texttt{EdgeC} \land
\texttt{ActivityC} \land \texttt{PairingC} \land
\texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that all molecules are divided into two types
using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
and any fusing set of molecules must have three molecules involved
from one type and one molecule from the other.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

\paragraph{Activity functions}
%
We also need to encode that the activity of the molecules are
controlled by activity functions.
%
The input VTS may include concrete activity functions for some molecules,
and for the others the functions may be unknown and to be synthesized. 
%
The concrete functions can be given to us in many different ways,
for example as a lookup table, or a concise Boolean formula.
%
In the following section, we will assume the appropriate encoding is
used for the concrete functions and represent them by \texttt{NodeFun}$_m$
and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.
%
%We will use $\nodef_m$ and $\edgef_m$ to represent functions that
%are unknown in a VTS.
%
% \begin{align}
% \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
% \tag{\texttt{ActiveN}}\label{eq:anb}\\
%    \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
%   \tag{\texttt{ActiveE}}\label{eq:aeb}
% \end{align}
%
%Later we will be synthesizing the unknown activity functions and 
%replace $\nodef_m$ and $\edgef_m$ with parameterized constraints that
%encode a space of candidate functions.
%\subsubsection{VTS properties}
%For the synthesis of incomplete systems,
%we need properties against which we synthesize the missing parts.
%
Next, we will discuss stability and $k$-connectedness.
%

\paragraph{Stability property}
%
We use Boolean variable $r_{i,j,m,p}$ to indicate if there is an
$m$-path from $i$ to $j$ of length less than or equal to $p$.
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is
$m$-reachable from node $i$ in less than $p$ steps.
%
Subsequently, we encode stability condition using the reachability variables.
\begin{align*}
\texttt{Paths}(r) &= \bigwedge\limits_{\mathclap{i,j,m,p}} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
\\
\texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
\\
\texttt{Stability} &= \exists r. \; \texttt{Paths}(r) \land \texttt{Loop}(r)
\end{align*}

\paragraph{$k$-connected property}
%
$k$-connectedness expresses robustness against failure of few edges.
%
Let us use $d_{i,j,q}$ to indicate $q$th edge between $i$ and $j$ is failed
and $r'_{i,j}$ to indicate if there is a path from $i$ to $j$ in
the modified VTS.
%
% To check whether $k$-connected is a
% necessary condition, we remove (drop) $k-1$ edges from the graph and
% if it disconnects the graph, and we get an assignment.
% %
% We have a graph that is not $k$-connected.
%
In the following, $\texttt{Fail}(d,k)$ encodes that only
existing edges can be failed and exactly $k-1$ edges are failed.
%
$\texttt{FReach}(d,r')$ defines reachability in the modified VTS.
%
We use a new variable $r'_{i,j,p}$ to encode reachability from
$i$ to $j$ in at most $p$ steps.
%
$\texttt{Connected}(r')$ says that all nodes are reachable from any
other node.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
% \texttt{ReachAbove}(d,r') = &
% \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}\\
\texttt{FReach}(d,r') = &\hspace{-1ex}
\bigwedge\limits_{i,j,p}  \hspace{-1ex}r^{\prime}_{i,j,p} \hspace{-1ex}\limplies\hspace{-1ex} [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \hspace{-1pt}\lor \hspace{-2pt} (\bigvee_{\mathclap{i' \neq i}}  r^{\prime}_{i',j,p-1} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ]\\
\texttt{Connected}(r') = & \Land\limits_{i,j} (r^{\prime}_{i,j,\nu} \lor r^{\prime}_{j,i,\nu})
\end{align*}
%We will be synthesizing $k$-connected graphs.
%
We define $\texttt{Connected}(k)$ that says for all possible valid failures
the graph remains reachable. 
\begin{align*}
\texttt{Connected}(k) = & \forall d.\;
(\texttt{Fail}(d,k) \limplies \exists r'.\;\texttt{FReach}(d,r')
\land \texttt{Connected}(r'))
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
Since $d$ variables in $\texttt{Connected}(k)$ are universally
quantified, $\texttt{Connected}(k)$ introduces quantifier alternations.
%
Therefore, synthesis against this property will require QBF reasoning.
%
We may make the formula quantifier free  by considering all possible failures
separately and introducing a vector of reachability variables for each
failure.
%
However, this will blow up the size of the formula and may not be
solvable by a SAT solver.
%

\subsection{Synthesis of VTS}
%In this section, we will present our synthesis method for
%the synthesis problems.

\subsubsection{Encoding Incomplete VTS}

In our synthesis method, we take a VTS $G =
(\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ as input.
%
We allow activity functions not to be specified.
%
We will use the same encoding for the VTS as discussed in the QBF subsection.
%
We construct the following constraints to encode the available information
about $G$.
%
We encode both the present and the absent components in $G$.
%
Later, the constraints will help us encode the synthesis problems.
%
\begin{align*}
\texttt{PresentE} &= \land \{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land q \leq q' \land m \in M_q \}\\
\texttt{PresentN} &= \land \{n_{i,m}| m \in \nlabel(i) \land i \in \nodes \}\\
\texttt{PresentP} &= \land \{p_{\{m_1,m_2,m_3,m_4\}}| \{m_1,m_2,m_3,m_4\} \in \pairs \} \\
\texttt{KnownActiveN} &= \land \{ a_{i,m} = \texttt{NodeFun}_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is defined.} \} \\
\texttt{KnownActiveE} &= \land \{ b_{i,j,q,m} = \texttt{EdgeFun}_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
| \edgef_m \text{ is defined.} \} \\
\texttt{PresentCons} & = \texttt{PresentE} \land \texttt{PresentN} \land 
\texttt{PresentP} \land \texttt{KnownActiveE} \land \\
&  \texttt{KnownActiveN}
\end{align*}
We also collect the variables that are not set to true in $\texttt{PresentCons}$.
\begin{align*}
\texttt{AbsentELabel} &=
\{e_{i,j,q,m}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
0 < q \leq q' \land m \not\in M_{q} \}\\
\texttt{AbsentE} &= \{e_{i,j,q}|(i,M_1,j),...,(i,M_{q'},j) \in \edges \land 
q' < q \leq \pi \}\\
\texttt{AbsentNLabel} &= \{n_{i,m}| m \not\in \nlabel(i) \land i \in \nodes \}\\
\texttt{AbsentP} &= \{p_{\{m_1,m_2,m_3,m_4\}}| {\{m_1,m_2,m_3,m_4\}} \not\in \pairs \} \\
\texttt{UnknownActive} &=  \Land \{ a_{i,m} = \nodef_m (n_{i,1},\dots,n_{i,\mu}) | \nodef_m \text{ is undefined.} \} \union \\
&\quad\quad\quad  \{ b_{i,j,q,m} = \edgef_m(e_{i,j,q,1}, .., e_{i,j,q,\mu})
| \edgef_m \text{ is undefined.} \}
\end{align*}
We have defined $\texttt{AbsentELabel}$, $\texttt{AbsentE}$, $\texttt{AbsentN}$, and
$\texttt{AbsentP}$
as sets.
%
They will be converted into formulas depending
on the different usage in the synthesis problems.

% Since not all the activity functions are defined some of the functions
% appearing in $\texttt{ActiveE}$ and $\texttt{ActiveN}$ are
% uninterpreted function symbols.

\subsubsection{Encoding synthesis constraints}

Now we will consider the encodings for the
listed synthesis problems.
%
The presented variations represent the encodings
supported by our tool.
%
Additionally, the combinations of the variation are also possible and
our tool easily supports them.
%
For simplicity of the presentation, we assume that if we are
synthesizing an aspect of VTS, then all other aspects are fully given.
%
Therefore, we will describe two kinds of constraints for synthesis
problems.
%
One will encode the variable part in the synthesis problem and
the other encodes the fixed parts.
%
Subsequently, the two constraints will be put together with 
$\texttt{Consistancy}$ and 
$\texttt{Property}$ to construct the constraints for synthesis.

\subsubsection{Fixing VTS by adding edges}
%
Now we will consider the case when we add new edges to VTS to satisfy the properties.
%
In the following, the pseudo-Boolean formula $\texttt{AddE}$ encodes
that at most $slimit$ new undeclared edges may be added in the VTS.
%
\texttt{FixedForEdge} encodes the parts of the VTS that are not allowed to change.
\begin{align*}
&\texttt{AddE}(slimit) = \sum~\texttt{AbsentE} \leq slimit\\
&\texttt{FixedForEdge} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad\quad\quad\quad \lnot \Lor \texttt{AbsentELabel} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}
\end{align*}
We put together the constraints and obtain the following formula.
\begin{align*}
& \texttt{SynthE}(slimit) =
\texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForEdge} \land
\texttt{AddE}(slimit)
% \tag{SynthE}\label{eq:addedge1}
\end{align*}
Similar to what we have seen $\texttt{Consistancy}$ encodes the basic constraints about VTS,
$\texttt{Property}$\; encodes the goal, and
the rest two are defined just above.
%
A satisfying model of $\texttt{SynthE}$ will make 
some of the edges in $\texttt{AbsentE}$ true such that~$\texttt{Property}$ is satisfied.
%
We limit the addition of the edges, since we look for a fix that require minimum number
of changes in the given VTS.
%
We start with $slimit = 1$ and grow one by one until $\texttt{SynthE}(slimit)$
becomes satisfiable.

In the later synthesis problems, we will construct a similar QBF
formula with same first two parts and the last two are due the
requirements of the synthesis problem.

\paragraph{\bf Fixing VTS by adding molecules to the labels:}
The system may also be fixed only by modifying labels on the edges or the nodes instead
of adding edges.
%
Here let us consider only adding molecules to the labels of edges.
%
In the following, the formula encodes that only $slimit$ edge labels may be added.
\begin{align*}
&\texttt{AddLabelEdge}(slimit) = 
\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthLabel}(slimit) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
\end{align*} 
Similar to the previous encoding, we solve the
satisfiability of the above formula to obtain additional molecules
that may be added to the edge labels to satisfy the properties.

\subsubsection{Fixing VTS by learning activity functions:}

Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

In the following, the formula \texttt{NNFTemplate} encodes a set of
negation normal form functions that take $y_1,..,y_\mu$ as input and
contain $\lambda$ literals.
%
We use $\texttt{Gate}$ to encode a gate that takes a parameter integer
$x$ to encode various gates.
%
We use $\texttt{Leaf} $ to encode the literal at some position.
%
Both are stitched to define \texttt{NNFTemplate}.
%
To encode the set of NNF formulas with $\lambda$ literals, it has
finite-range integer variables
$z_1,..,z_{2\lambda}$ as parameters.

% \paragraph{Encoding low depth cnf circuits}
% \paragraph{Encoding boolean gates}

\begin{align*}
&\texttt{Gate}( x, w_1, w_2 ) = ( x  = 1 \limplies w_1  \land w_2 ) \land  
( x = 2  \limplies w_1  \lor w_2 ) \\
&\texttt{Leaf}( x, [y_1,..,y_\mu] ) =
\Land\limits_{l=1}^{\mu} ( x = 2l-1  \limplies y_{l}) \land ( x = 2l  \limplies \lnot y_{l})\\
&\texttt{NNFTemplate}([z_1,..,z_{2\lambda}],[y_1,..,y_\mu] ) = \\
&\exists w_1,..,w_{2\lambda}.\;w_1 \land \Land_{l=1}^{\lambda} w_{\lambda+l} = \texttt{Leaf}( z_{\lambda+l}, [y_1,..,y_\mu] ) \land
w_{l} = \texttt{Gate}( z_l, w_{2l},w_{2l+1})
\end{align*}

Using the template we define the constraints $\texttt{FindFunctions}(z,\lambda)$
that encodes the candidate functions that satisfy the activity requirements,
where $z$ is the vectors of parameters for encoding parameters
for each molecule,
and $\lambda$ limits the size of the candidate functions. 
%
We fix the all other aspects of the VTS to be fixed via constraints
$\texttt{FixedForFunctions}$.
%
\begin{align*}
&\texttt{FindFunctions}(z,\lambda) =\\
&\Land \{ \bigwedge\limits_{i} n_{i,m} \limplies a_{i,m} = 
\texttt{NNFTemplate}([z_{m,1},..,z_{m,2\lambda}],[n_{i,1},\dots,n_{i,\mu}] ) \\
& \hspace{8cm}|
\nodef_m \text{ is undefined}\} \\
&\Land \{ \bigwedge\limits_{i,j,q} e_{i,j,q,m} \limplies b_{i,j,q,m} = 
\texttt{NNFTemplate}([z_{i,j,q,1},..,z_{i,j,q,2\lambda}],[e_{i,j,q,1},..,e_{i,j,q,\mu}] ) \\
& \hspace{8cm} | \edgef_m \text{ is undefined}
\}\\
& \texttt{FixedForFunctions} = \texttt{PresentCons} \land\\
& \quad \quad
\lnot \Lor \texttt{AbsentE} \;\union\; \texttt{AbsentELabel} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthFunction}(z,\lambda) = \\
& \quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForFunctions} \land \texttt{FindFunctions}(slimit) )
\end{align*}
We construct $\texttt{SynthFunction}(z,\lambda)$ similar to the earlier
variations.
%
By reading of the values of $z$ in a satisfying model of the formula,
we learn the synthesized function.

\subsubsection{Fixing VTS by both adding/deleting parts:}
%
Now we will consider repairing of VTS by allowing not only addition but also
deletion of the molecules, edges, functions, or pairing matrix.
%
We have encoded the repairing in our tool by introducing flip bits
for each variable that is modifiable in the VTS.
%
We illustrate the repairing on one class of variables and rest can be
easily extended.
%
Let us consider repairing of node labels.
%
For each bit $n_{i,m}$, we create a bit $flip_{i,m}$.
%
We add constraints that take xor of VTS assigned values for  $n_{i,m}$
and $flip_{i,m}$.
%
We also limit the number of $flip_{i,m}$ that can be true, therefore
limiting the number of flips.
%
The above constraints are encoded in $\texttt{FlipN}(slimit)$.
\begin{align*}
&\texttt{FlipN}(slimit,flip) = \Land \{n_{i,m}\lxor flip_{i,m}| m \in \nlabel(i) \land i \in \nodes \} \land \\
& \quad \quad \quad
\Land \{ \lnot n_{i,m}\lxor flip_{i,m}| m \not \in \nlabel(i) \land i \in \nodes \} \land  \sum\limits_{i,m} flip_{i,m} \leq slimit
\end{align*}
%
Similar to the earlier variations, we construct
$\texttt{SynthRepairNode}(slimit)$ for the repair.
%
In that, $\texttt{FixedForNodeRepair}$ encodes all the parts of VTS that do not change.
\begin{align*}
% \\ 
& \texttt{FixedForNodeRepair} =  \texttt{PresentE} \land  
\texttt{PresentP} \land \texttt{KnownActiveE} 
\land \\
& \quad \texttt{UnknownActive} \land \texttt{KnownActiveN} \land \lnot 
\Lor \texttt{AbsentE} \;\union\; \texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthRepairNode}(slimit,flip) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForNodeRepair} \land \texttt{FlipN}(slimit,flip) )
\end{align*}
A satisfying model of $\texttt{SynthRepairNode}(slimit,flip)$ will assign some
$flip$ bits to true.
We will learn from the assignments the needed modifications in the VTS.

### 2018-11-15 papers/journal/problem.tex
added QBF section and attached Synthesis encodings to it

>>>>

 \todo{A dummy template} \textbf{QBF search problem:}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$,and
$G$ is not $k$-connected.

%
%In this section, we will present a list of synthesis problems that may
%arise from the partially available information about a VTS and our synthesis method
%for the problems.

%\subsection{Problem Statements}
\textbf{Synthesis problem statement:}
We will assume that we are given a VTS, whose all components
are not specified.
%
Our objective is to find the missing parts.
%
The missing parts can be in any of the components of VTS. 
%
For example, some undiscovered edges or nodes, or insufficient
knowledge about the presence of molecules in some part of the VTS.
%
To cover most of the likely variations of this missing information,
we have encoded the following variants of VTS synthesis problem.

\begin{enumerate}
	\item Fixing VTS by adding edges 
	\item Fixing VTS by adding molecules to the labels
	\item Fixing VTS by learning activity functions
	% \begin{enumerate}
	%   \item kcnf: low depth circuit.
	%   \item Boolean gates: And, Or.
	%   \item Boolean gates with linear combination.  
	% \end{enumerate}        
	% - Function dependence with var occurring once.
	\item  Fixing VTS by both adding/deleting parts
\end{enumerate}

\subsubsection{Encoding synthesis property}

We will do synthesis against the following property that says the VTS
is stable and 3-connected.
%
% The property is designed to balance the search space such that the synthesis procedure does not
% succeed with simply adding too many edges. 
%
\begin{align*}
\texttt{Property} =  \texttt{Stability} \land \texttt{Connected}(3) 
%\land \texttt{DisConnected}(4)
\end{align*}
The property was proposed in~\cite{shukla2017discovering}.
%
However, the biological relevance of the property is debatable and open for change.
%
Our tool is easily modifiable to support any other property that may be deemed 
interesting by the biologists.
